### 2021-10-11 documents/floats/defecate.tex
cleaned up data, started work on discussion section

\begin{table}
\centering
\caption{\rc{weka} \qu{to defecate} as another class-switching \gl{s_p_} verb \parencites[418]{courtz2008carib}[455]{maquiritaricaceres2011}[44]{souza1993arara}[118]{alves2013verbo}[86, 206]{wayanatavares2005}[294]{triomeira1999}{meira2005bakairi}[96]{camargo2002lexico}[319; p.c., Spike Gildea]{mattei1994diccionario}}
\label{tab:defecate}
\begin{tabular}[t]{@{}lll@{}}
\toprule
Language &           Form &                  Class \\
\midrule
\kaxui   &     \obj{weka} &              \gl{s_p_} \\
\arara   &    \obj{watke} &              \gl{s_p_} \\
\ikpeng  &     \obj{atke} &              \gl{s_p_} \\
\bakairi &     \obj{əeke} &              \gl{s_a_} \\
\trio    &     \obj{weka} &              \gl{s_a_} \\
\wayana  &     \obj{uika} &  \gl{s_a_} / \gl{s_p_} \\
\apalai  &     \obj{weka} &                      ? \\
\kalina  &    \obj{uweka} &              \gl{s_p_} \\
\maqui   &     \obj{weka} &              \gl{s_p_} \\
\panare  &  \obj{(a)iʔka} &                      ? \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[\rc{weka} \qu{to defecate} as another class-switching \gl{s_p_} verb]{\rc{weka} \qu{to defecate} as another class-switching \gl{s_p_} verb \parencites[418]{courtz2008carib}[455]{maquiritaricaceres2011}[44]{souza1993arara}[118]{alves2013verbo}[86, 206]{wayanatavares2005}[294]{triomeira1999}{meira2005bakairi}[96]{camargo2002lexico}[319; p.c., Spike Gildea]{mattei1994diccionario}}
\label{tab:defecate}
\begin{tabular}[t]{@{}lll@{}}
\toprule
Language &           Form &                  Class \\
\midrule
\apalai  &     \obj{weka} &                      ? \\
\arara   &    \obj{watke} &              \gl{s_p_} \\
\bakairi &     \obj{əeke} &              \gl{s_a_} \\
\ikpeng  &     \obj{atke} &              \gl{s_p_} \\
\kalina  &    \obj{uweka} &              \gl{s_p_} \\
\kaxui   &     \obj{weka} &              \gl{s_p_} \\
\maqui   &     \obj{weka} &              \gl{s_p_} \\
\panare  &  \obj{(a)iʔka} &                      ? \\
\trio    &     \obj{weka} &              \gl{s_a_} \\
\wayana  &     \obj{uika} &  \gl{s_a_} / \gl{s_p_} \\
\bottomrule
\end{tabular}
\end{table}

### 2021-10-11 documents/floats/imperatives.tex
cleaned up data, started work on discussion section

\begin{tabular}[t]{@{}lll@{}}
\toprule
Language &                         \gl{s_a_} &                             \gl{s_p_} \\
\midrule
\hixka  &          \obj{omoh-ko} \qu{come!} &  \obj{\emp{oj-}okajɨm-ko} \qu{go up!} \\
\arara  &  \obj{odotpot-ko} \qu{come back!} &      \obj{\emp{o-}alum-ko} \qu{jump!} \\
\trio   &          \obj{epɨ-kə} \qu{bathe!} &   \obj{\emp{ə-}eremina-kə} \qu{sing!} \\
\wayana &         \obj{əməm-kə} \qu{enter!} &    \obj{\emp{əw-}eremi-kə} \qu{sing!} \\
\apalai &           \obj{otuʔ-ko} \qu{eat!} &      \obj{\emp{o-}nɨʔ-ko} \qu{sleep!} \\
\kalina &         \obj{oʔmaʔ-ko} \qu{stop!} &   \obj{\emp{aj-}awon-ko} \qu{get up!} \\
\panare &            \obj{ape-ʔ} \qu{flee!} &             \obj{ahpən-kə} \qu{jump!} \\
\bottomrule
\end{tabular}

>>>>

\begin{table}
\centering
\caption[Imperatives of \gl{s_a_} and \gl{s_p_} verbs]{Imperatives of \gl{s_a_} and \gl{s_p_} verbs \parencites[62]{koehn1986apalai}[Mopo/20]{koehns1994textos}[44, 89]{derbyshire1965textos}[5, 17]{mattei1994diccionario}[190]{hoff1968carib}[161]{alves2017arara}[323]{triomeira1999}[227]{wayanatavares2005}}
\label{tab:imperatives}
\begin{tabular}[t]{@{}lll@{}}
\toprule
Language &                         \gl{s_a_} &                             \gl{s_p_} \\
\midrule
\apalai &           \obj{otuʔ-ko} \qu{eat!} &      \obj{\emp{o-}nɨʔ-ko} \qu{sleep!} \\
\hixka  &          \obj{omoh-ko} \qu{come!} &  \obj{\emp{oj-}okajɨm-ko} \qu{go up!} \\
\panare &            \obj{ape-ʔ} \qu{flee!} &             \obj{ahpən-kə} \qu{jump!} \\
\kalina &         \obj{oʔmaʔ-ko} \qu{stop!} &   \obj{\emp{aj-}awon-ko} \qu{get up!} \\
\arara  &  \obj{odotpot-ko} \qu{come back!} &      \obj{\emp{o-}alum-ko} \qu{jump!} \\
\trio   &          \obj{epɨ-kə} \qu{bathe!} &   \obj{\emp{ə-}eremina-kə} \qu{sing!} \\
\wayana &         \obj{əməm-kə} \qu{enter!} &    \obj{\emp{əw-}eremi-kə} \qu{sing!} \\
\bottomrule
\end{tabular}
\end{table}

### 2021-10-11 documents/floats/nominalizations.tex
added additional split-s data, bakairi examples, rewrote up to sec 3.4
cleaned up data, started work on discussion section

\begin{tabular}[t]{@{}lll@{}}
\toprule
Language &                                         \gl{s_a_} &                                             \gl{s_p_} \\
\midrule
\kaxui  &       \obj{o-\emp{w-}ehurka-tpɨrɨ} \qu{your fall} &            \obj{o-onenmehɨ-tpɨrɨ} \qu{your waking up} \\
\arara  &        \obj{\emp{w-}orik-tubo} \qu{dancing place} &              \obj{ereŋmɨ-tpo} \qu{killing instrument} \\
\trio   &   \obj{ji-\emp{w-}əturu-to} \qu{(for) my talking} &              \obj{j-emamina-to} \qu{(for) my playing} \\
\wayana &          \obj{ɨ-\emp{w-}əturu-topo} \qu{my story} &        \obj{j-ɨnɨkɨ-topo} \qu{my object for sleeping} \\
\apalai &            \obj{j-epɨ-topo} \qu{my bathing place} &   \obj{j-enuru-topõ-pɨrɨ} \qu{the place of my birth} \\
\kalina &  \obj{a-\emp{w-}ekupi-rɨ} \qu{your taking a bath} &                  \obj{aj-ereʔna-∅} \qu{your fainting} \\
\panare &     \obj{j-\emp{u-}t͡ʃireema-n} \qu{their eating} &  \obj{tj-arunkampətɨ-n} \qu{his hair standing on end} \\
\bottomrule
\end{tabular}

>>>>

\begin{table}
\centering
\caption[Nominalizations of \gl{s_a_} and \gl{s_p_} verbs]{Nominalizations of \gl{s_a_} and \gl{s_p_} verbs \parencites[90]{koehn1986apalai}[ner2-003]{koehns1994textos}[390]{panarepayne2013}[23]{mattei1994diccionario}[135, 392]{hoff1968carib}[97]{alves2017arara}[49, 74]{schuring2018kaxuyana}[246]{triomeira1999}[130, 409]{wayanatavares2005}}
\label{tab:nominalizations}
\begin{tabular}[t]{@{}lll@{}}
\toprule
Language &                                         \gl{s_a_} &                                             \gl{s_p_} \\
\midrule
\apalai &            \obj{j-epɨ-topo} \qu{my bathing place} &   \obj{j-enuru-topõ-pɨrɨ} \qu{the place of my birth} \\
\panare &     \obj{j-\emp{u-}t͡ʃireema-n} \qu{their eating} &  \obj{tj-arunkampətɨ-n} \qu{his hair standing on end} \\
\kalina &  \obj{a-\emp{w-}ekupi-rɨ} \qu{your taking a bath} &    \obj{aj-ereʔna-{\normalfont ∅}} \qu{your fainting} \\
\arara  &        \obj{\emp{w-}orik-tubo} \qu{dancing place} &              \obj{ereŋmɨ-tpo} \qu{killing instrument} \\
\kaxui  &       \obj{o-\emp{w-}ehurka-tpɨrɨ} \qu{your fall} &            \obj{o-onenmehɨ-tpɨrɨ} \qu{your waking up} \\
\trio   &   \obj{ji-\emp{w-}əturu-to} \qu{(for) my talking} &              \obj{j-emamina-to} \qu{(for) my playing} \\
\wayana &          \obj{ɨ-\emp{w-}əturu-topo} \qu{my story} &        \obj{j-ɨnɨkɨ-topo} \qu{my object for sleeping} \\
\bottomrule
\end{tabular}
\end{table}

### 2021-10-11 documents/sections/proto_carib.tex
cleaned up data, started work on discussion section

Many languages show an \gl{s_a_} class marker in deverbalized forms, which can be reconstructed to \PC as \rc{w-}.\footnote{See \textcite[227]{meira2000split}, who identifies reflexes of this morpheme as having \dbqu{no purpose other than being \qu{class markers}, without any obvious semantic or functional load}.}
With \gl{s_a_} verbs, \rc{w-} occurred immediately between the possessive prefixes and the verb stem, while \gl{s_p_} verbs took the bare prefixes.
Reflexes of \rc{w-} in languages from different branches are illustrated in \cref{tab:participles} for participles, and in \cref{tab:nmlz} for nominalizations.
%\kaxui does not preserve \rc{w-} in its participles (\obj{tehurkat͡ʃe} \qu{fallen}, not \ungr{tɨwehurkat͡ʃe}), while \apalai only preserves it there, but not in nominalizations (\obj{jepɨtopo} \qu{my bathing place}, not \ungr{joepɨtopo}).

\begin{table}
	\centering
	\caption{Participles of \gl{s_a_} and \gl{s_p_} verbs \parencites[118, 207]{alves2017arara}[30, 42]{camargo2002lexico}[430, 433]{hoff1968carib}[333, 334]{triomeira1999}[400]{wayanatavares2005}[39]{schuring2018kaxuyana}[232, 244]{panarepayne2013}}
	\label{tab:participles}
\input{floats/participles}
\end{table}

\begin{table}
	\centering
	\caption{Nominalizations of \gl{s_a_} and \gl{s_p_} verbs \parencites[49, 74]{schuring2018kaxuyana}[97]{alves2017arara}[246]{triomeira1999}[130, 409]{wayanatavares2005}[90]{koehn1986apalai}[ner2-003]{koehns1994textos}[135, 392]{hoff1968carib}[390]{panarepayne2013}[23]{mattei1994diccionario}}
	\label{tab:nmlz}
	\input{floats/nominalizations}
\end{table}

%\begin{table}
%	\centering
%	\caption{Nominalizations of \gl{s_a_} and \gl{s_p_} verbs}
%	\label{tab:nmlz}
%	\begin{tabular}{@{}llll@{}}
%	\mytoprule
%Language & \gl{s_a_} verb & \gl{s_p_} verb & Source(s)\\
%	\mymidrule
%\kaxui & \obj{o-\emp{w-}ehurka-tpɨrɨ} \qu{your fall} & \obj{o-onenmehɨ-tpɨrɨ} \qu{your waking up} & \textcite[49, 74]{schuring2018kaxuyana}\\
%\arara & \obj{\emp{w-}orik-tubo} \qu{dancing place} & \obj{ereŋmɨ-tpo} \qu{killing instrument} & \textcite[97]{alves2017arara} \\
%\trio & \obj{ji-\emp{w-}əturu-to} \qu{(for) my talking} & \obj{j-emamina-to} \qu{(for) my playing} & \textcite[246]{triomeira1999} \\
%\wayana & \obj{ɨ-\emp{w-}əturu-topo} \qu{my story} & \obj{j-ɨnɨkɨ-topo} \qu{my object for sleeping} & \textcite[409, 130]{wayanatavares2005}\\
%\kalina & \obj{a-\emp{w-}ekupi-rɨ} \qu{your taking a bath} & \obj{aj-ereʔna-Ø} \qu{your fainting} & \textcite[392, 135]{hoff1968carib}\\
%\apalai & \obj{j-epɨ-topo} \qu{my bath place} & \obj{j-enuru-topõ-pɨrɨ} \qu{the place of my birth} & \textcites[90]{koehn1986apalai}[ner2/1]{koehns1994textos}\\
%\panare & \obj{j-\emp{u-}t͡ʃireema-n} \qu{their eating} & \obj{tj-arunkampətɨ-n} \qu{his hair standing on end} & \textcites[390]{panarepayne2013}[23]{mattei1994diccionario}\\
%	\mybottomrule
%	\end{tabular}
%\end{table}

The distinction between \gl{s_a_} and \gl{s_p_} is also borne out in imperatives, the suffix for which can be reconstructed as \PC \rc{-kə}.
Here, \gl{s_p_} verbs took the \gl{p}-oriented second person prefix \rc{ə(j)-}, while \gl{s_a_} verbs were unprefixed.
This is illustrated with reflexes in various modern languages in \cref{tab:imp}.
As in the case of the \gl{s_a_} marker \rc{w-} participles and nominalizations, some languages have lost the distinction between \gl{s_a_} and \gl{s_p_} verbs in imperatives, for example \panare.

\begin{table}
	\centering
	\caption{Imperatives of \gl{s_a_} and \gl{s_p_} verbs \parencites[44, 89]{derbyshire1965textos}[161]{alves2017arara}[323]{triomeira1999}[227]{wayanatavares2005}[62]{koehn1986apalai}[Mopo/20]{koehns1994textos}[190]{hoff1968carib}[5, 17]{mattei1994diccionario}}
	\label{tab:imp}
	\input{floats/imperatives}
\end{table}

>>>>

Many languages show an \gl{s_a_} class marker in deverbalized forms, which can be reconstructed to \PC as \rc{w-}.\footnote{See \textcite[227]{meira2000split}, who identifies reflexes of this morpheme as having \dbqu{no purpose other than being \qu{class markers}, without any obvious semantic or functional load}.}
With \gl{s_a_} verbs, \rc{w-} occurred immediately between the possessive prefixes and the verb stem, while \gl{s_p_} verbs took the bare prefixes.
Reflexes of \rc{w-} in languages from different branches are illustrated in \cref{tab:participles} for participles, and in \cref{tab:nominalizations} for nominalizations.
%\kaxui does not preserve \rc{w-} in its participles (\obj{tehurkat͡ʃe} \qu{fallen}, not \ungr{tɨwehurkat͡ʃe}), while \apalai only preserves it there, but not in nominalizations (\obj{jepɨtopo} \qu{my bathing place}, not \ungr{joepɨtopo}).

\input{floats/participles}

\input{floats/nominalizations}

The distinction between \gl{s_a_} and \gl{s_p_} is also borne out in imperatives, the suffix for which can be reconstructed as \PC \rc{-kə}.
Here, \gl{s_p_} verbs took the \gl{p}-oriented second person prefix \rc{ə(j)-}, while \gl{s_a_} verbs were unprefixed.
This is illustrated with reflexes in various modern languages in \cref{tab:imperatives}.
As in the case of the \gl{s_a_} marker \rc{w-} participles and nominalizations, some languages have lost the distinction between \gl{s_a_} and \gl{s_p_} verbs in imperatives, for example \panare.

\input{floats/imperatives}
